Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-19 paper/sections/proof-reconstruction.tex
[ paper ] minor changes.

To convert a general recursive call into a structurally recursive call, we use
the \emph{Bounded Recursion} technique presented in \cite{Coquand1992} but others found in
\cite{Coquand1992,Abel2002,Bove2005} could be used.

The \emph{Bounded Recursion} technique converts a general recursive
function into a structural recursive function by adding an additional
argument that handle the times the function can call itself.

In our case, we add a natural number $n : \Nat$ in the input of the general
recursive function for such an argument in mostly cases, and perform the
recursion over the structure of \Nat type. \abbre{Nat} type is the usual
type with \zero and \suc constructors, and including the common arithmetic
operations ($+,\,-,\,*$) and representations of $\zero, \suc, \suc(\zero),
\dots$
with $0,1,2,\dots$.

>>>>

To convert a general recursive call into a structurally recursive call, we use
the \emph{Bounded Recursion} technique presented in \cite{Bertot2004} but
others found in \cite{Coquand1992,Abel2002,Bove2005} could be used.
This technique converts a general recursive
function into a structural recursive function by adding an additional
argument that handle the times the function can call itself.
As we show later, we use the complexity of the original function for the new argument in the new function.

For that argument, we add the natural number $n : \Nat$ in the input of the
general recursive function, and perform the recursion over the structure of
\Nat type. \abbre{Nat} type is the usual type with \zero and \suc constructors, and including the common arithmetic operations ($+,\,-,\,*$) and
representations of $\zero, \suc, \suc(\zero), \dots$ with $0,1,2,\dots$.
